Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
temp p and include nobs in temp

<!-- temp -->
The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information. 
<!-- TODO: results

Edge overlap
was higher during fall, winter and spring (approximately October - June) than in
summer (approximately June - October)  (Figure \@ref(fig:temp) A). Similarly,
individual graph strength was also higher in these periods (Figure
\@ref(fig:temp) C). These periods of increased sociality correspond to seasons of
heterogeneous resource availability [Peigner_2019].

By explicitly considering
the temporal context of social interactions in separate layers, multilayer
networks provide a detailed and dynamic perspective of animal social networks.
In addition, this could be extended using time-aggregated networks and a
moving-window approach to inform the temporal scale including time window size
and sampling effort [@Farine_2017; @Bonnell_2020]. 
-->

For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015].

Bison
(*Bison bison*) showed stronger habitat selection in larger groups, and
avoidance of predation risk was a main factor contributing to their habitat
selection [@Fortin_2009]. These examples, comparing sociality and habitat
selection across spatial and temporal contexts, are implicitly multilayer
analyses.

<!-- nobs -->
It is crucial to include sufficient data within sampling periods or time windows
to construct robust networks <!--TODO check--> [@Farine_2017; Proskurnikov_2017]. To test the
influence of data quantity on multilayer networks, we generate multilayer networks
using a subset of observations. Variance decreased across all
network metrics in all three habitat layers with increasing number of
observations. Individual graph strength showed high variability at low number of
observations, while edge overlap and multidegree increased sharply. After
approximately 200 observations, the rate of change for all metrics decreased and
and graph strength remained relatively static, while edge overlap and
multidegree continued to increase slowly. As more observations were added, rarer
relationships were recorded revealing the value of this form of sensitivity
analysis. Finally, due to the autocorrelated nature of biologging data it is
essential to ensure social association data area non-randomly distributed
[@Farine_2017b].
<!-- nobs -->

>>>>

<!-- temp -->
<!-- TODO: results

In addition, this could be extended using time-aggregated networks and a
moving-window approach to inform the temporal scale including time window size
and sampling effort [@Farine_2017; @Bonnell_2020]. 
-->
The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information. 
We found increased edge overlap in fall, winter and spring (approximately October - 
June) than in summer (approximately June - October) (Figure \@ref(fig:temp) A). 
Similarly, individual graph strength was also higher in these periods 
(Figure \@ref(fig:temp) C). These periods of increased sociality correspond 
to seasons of heterogeneous resource availability [Peigner_2019]. By explicitly 
considering the temporal context of social interactions in separate layers, multilayer
networks provide a detailed and dynamic perspective of animal social networks.
For example, female mandrill (*Mandrillus sphinx*) sociality is more completely
represented using temporal multilayer networks than aggregated networks 
[@Pereira_2020]. Evans et al. [-@Evans_2020]
observed seasonal differences in the social structure of mice 
(*Mus musculus domesticus*) related to temperature and breeding activity. 
Finally, it is crucial to include sufficient data within sampling periods or time windows
to construct robust networks [@Farine_2017; Proskurnikov_2017]. We found
variance decreased in edge overlap and multidegree across habitat layers as well
as in graph strength within habitat layers with increasing number of 
observations (Figure \@ref(fig:nobs)). As more observations were added, rarer
relationships were recorded revealing the value of this form of sensitivity
analysis.

<!-- Finally, due to the autocorrelated nature of biologging data it is -->
<!-- essential to ensure social association data area non-randomly distributed -->
<!-- [@Farine_2017b]. -->
